Array Programming with NumPy

### 2020-05-25 body.tex
Simplify tex for submission

Now, fifteen years later, NumPy underpins almost every Python library that does scientific or
numerical computation \cite{dubois2007guest,oliphant2007python,millman2011python,perez2011python}
including SciPy \cite{virtanen2020scipy},
Matplotlib \cite{hunter2007matplotlib}, pandas \cite{mckinney-proc-scipy-2010},
scikit-learn \cite{pedregosa2011scikit}, and
scikit-image \cite{vanderwalt2014scikit}.
It is a community-developed, open-source library, which provides a
multidimensional Python array object along with array-aware functions
that operate on it.
Because of its inherent simplicity, the NumPy array is
the \emph{de facto} exchange format for array data in Python.

>>>>

Now, fifteen years later, NumPy underpins almost every Python library that does scientific or
numerical computation including SciPy \cite{virtanen2020scipy},
Matplotlib \cite{hunter2007matplotlib}, pandas \cite{mckinney-proc-scipy-2010},
scikit-learn \cite{pedregosa2011scikit}, and
scikit-image \cite{vanderwalt2014scikit}.
It is a community-developed, open-source library, which provides a
multidimensional Python array object along with array-aware functions
that operate on it.
Because of its inherent simplicity, the NumPy array is
the \emph{de facto} exchange format for array data in Python.

### 2020-05-25 methods.tex
Simplify tex for submission

@@

\section*{Library organization}

@@

\subsection*{Core}

The \texttt{ndarray} data structure and the
universal functions make up the core of NumPy.

@@

\subsection*{Computing libraries.}

NumPy provides a large library of functions for array manipulation
and scientific computing, including functions for: creating, reshaping,
concatenating, and padding arrays; searching, sorting and counting data
in arrays; computing elementary statistics, such as the mean, median,
variance, and standard deviation; file I/O; and more.

@@

\subsection*{Infrastructure libraries}

NumPy provides utilities for writing tests and for building Python packages.

@@

\subsection*{F2PY}  The program \texttt{f2py} is a tool for
building NumPy-aware Python wrappers of Fortran functions.
NumPy itself does not use any Fortran code;  F2PY is part of NumPy
for historical reasons.

\section*{Governance}

@@

\section*{Funding}

@@

\section*{Developers}

@@

\section*{Community calls}

@@

\section*{NumPy enhancement proposals}

@@

\section*{Central role}

@@

\section*{Wheels build system}

@@

\section*{Recent technical improvements}

@@

\section*{Array function protocol}

@@

\section*{Random number generation}

@@

\section*{Testing on multiple architectures}

>>>>

\section*{Methods}

@@

\subsection*{Library organization}

@@

\paragraph{\emph{Core.}}  The \texttt{ndarray} data structure and the
universal functions make up the core of NumPy.

@@

\paragraph{\emph{Computing libraries.}}
NumPy provides a large library of functions for array manipulation
and scientific computing, including functions for: creating, reshaping,
concatenating, and padding arrays; searching, sorting and counting data
in arrays; computing elementary statistics, such as the mean, median,
variance, and standard deviation; file I/O; and more.

@@

\paragraph{\emph{Infrastructure libraries.}} NumPy provides utilities
for writing tests and for building Python packages.

@@

\paragraph{\emph{F2PY.}}  The program \texttt{f2py} is a tool for
building NumPy-aware Python wrappers of Fortran functions.
NumPy itself does not use any Fortran code;  F2PY is part of NumPy
for historical reasons.

\subsection*{Governance}

@@

\subsection*{Funding}

@@

\subsection*{Developers}

@@

\subsection*{Community calls}

@@

\subsection*{NumPy enhancement proposals}

@@

\subsection*{Central role}

@@

\subsection*{Wheels build system}

@@

\subsection*{Recent technical improvements}

@@

\subsection*{Array function protocol}

@@

\subsection*{Random number generation}

@@

\subsection*{Testing on multiple architectures}

### 2020-05-25 paper.tex
Simplify tex for submission

% Packages
\usepackage{moreverb} % for verbatim ouput (for wordcount)

@@

\usepackage[switch]{lineno}
\linenumbers

@@

% Count of words
%\verbatiminput{wordcount.tex}

>>>>

% Packages
\usepackage{listings, textcomp}
\lstset{language=Python}

\lstset{ %
  basicstyle=\ttfamily\footnotesize,  % size of fonts used for the code
  xleftmargin=\parindent,
  breaklines=true,   % automatic line breaking only at whitespace
  captionpos=b,   % sets the caption-position to bottom
  commentstyle=\color{gray},  % comment style
  keywordstyle=\color{blue},  % keyword style
  stringstyle=\color{red},  % string literal style
  upquote=true  %straight single quotes (requires textcomp)
}

@@

@@
